\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage{natbib}
\usepackage{bibentry}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}
\nobibliography{../myPubs/myPubs.bib, ../myPosters/myPosters.bib}
\bibliographystyle{ieeetr}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE G. William Chapman IV}} & Email: \href{mailto:g.william.chapman.iv@gmail.com}{g.william.chapman.iv@gmail.com}\\
  \href{https://wchapman.github.io/}{website: https://wchapman.github.io/} \\%& Mobile:~~~+1-617-383-9042 \\
\end{tabular*}

\section{Summary}
Researcher in neuromorphic machine learning for hardware constrained online learning.
With an additional six years experience as a software developer and scientific analyst for data intensive research application.
As a scientific analyst I have specialized in temporally-aware analysis, with a strong emphasis on interacting with subject-experts.
As an independent researcher, I have focused on novel deep learning architectures to support time series prediction, computer vision, spatial navigation, and symbolic reasoning. 



%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Boston University}{Boston, MA}
      {Doctor of Philosophy - Computational Neuroscience}{May 2023}
    \resumeSubheading
      {University of Colorado}{Boulder, CO}
      {Master of Arts - Cognitive Neuroscience}{May 2018}
    \resumeSubheading
      {Boston University}{Boston, MA}
      {Bachelor of Science - Biomedical Engineering, Minor in Electrical Engineering}{May 2012}
\resumeSubHeadingListEnd
	    
%\vspace{-5pt}
\section{Skills}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{Python, MATLAB, Bash, SQL, R, \LaTeX}
	\resumeSubItem{Frameworks}{Scikit Learn, PyTorch, Pandas, Numpy, Slurm, SGE, Git}
	\resumeSubItem{General}{Machine Learning, Deep Learning, Time Series Prediction, Advanced Statistical Analysis, Dynamical Systems, Biomedical Engineering, Project Management, Scientific \& Data Communication}
\resumeSubHeadingListEnd

\vspace{-5pt}
\section{Experience}
  \resumeSubHeadingListStart
  \resumeSubheading{Sandia National Labs}{Albuquerque, NM}
    {Postdoctoral Appointee, Neuromorphic Computing}{2023 - Present}
    \resumeItemListStart
    \resumeItemListEnd

    \resumeSubheading{Boston University}{Boston, MA}
    {Graduate Research Fellow}{2018 - 2023}
    \resumeItemListStart
      \resumeItem{Biological Predictive Coding}{Created a novel, biologically inspired, machine learning architecture and learning rule for temporal prediction. Functions above state-of-the-art for both short-term and long-term time series prediction, with applications for lifelong learning, and generalization.}
      \resumeItem{Egocentric-Allocentric Transformations}{Designed an explainable ML model which receives self-centered sensor and motor information, fusing sensor information through recurrent hidden layers. Hidden layers create explicit reference-frame transformations, in addition to low-dimensional latent representations.}
      \resumeItem{Symbolic Predictive Learning}{Created a novel architecture which utilizes predictive coding and dynamic attentional routing to solve a symbolic reasoning task.}
    \resumeItemListEnd

    \resumeSubheading{eCortex \& University of Colorado}{Boulder, CO}
    {Neural Modeler}{2016 - 2018}
    \resumeItemListStart
      \resumeItem{Symbolic Reasoning}{Extended existing computational models of working memory to create a model capable of simple symbolic processing, utilizing attentional mechanisms.}
      \resumeItem{Electrophysiology}{Designed and ran a corresponding EEG experiment to test model predictions. Created novel causal frequency-time analyses to determine timecourse of functional connectivity.}
    \resumeItemListEnd

    \resumeSubheading{Center for Systems Neuroscience}{Boston, MA}
    {Research Software Engineer}{May 2012 - August 2016}
    \resumeItemListStart
        \resumeItem{Software Design}
        {Primary designer for centralized OOP software for standardized data storage and exploratory analyses of neural and behavioral data across multiple labs, which is now used at over half a dozen independent research locations.}
        \resumeItem{Data Pipelines}
        {Created standardized data pipelines for preprocessing various unstructured data and combining into a centralized SQL database, automated by cloud-computing frameworks.}
        \resumeItem{Data Analysis}{Primary statistical analysis expert for over ten peer-reviewed publications in systems and computational neuroscience, including time-series analysis, frequentist statistics, generalized linear models, and data visualization.}
      \resumeItemListEnd

\vspace{-5pt}
    \resumeSubheading
		{Boston Medical Center}{Boston, MA}
		{Neuroimaging Research Assistant}{May 2009 -  May 2012}
		\resumeItemListStart
        \resumeItem{Alzheimer's Disease}{Primary individual for data pipelines and novel analysis of structural MRI and behavioral data, leading to predictive models of clinical Alzheimer's Disease progression.}
		\resumeItemListEnd

\resumeSubHeadingListEnd

\pagebreak
\vspace{-5pt}
\section{Teaching Experience}
\resumeSubHeadingListStart

    \resumeSubheading{Boston University}{Boston, MA}
    {Graduate Teaching Fellow}{2018 - 2020}
    \resumeItemListStart
      \resumeItem{Cognitive Neuroscience \& Learning and Memory}{Led weekly discussion groups, reviewing and previewing material; created exams.}
    \resumeItemListEnd

    \resumeSubheading{University of Colorado}{Boulder, CO}
    {Graduate Teaching Fellow}{2016 - 2018}
    \resumeItemListStart
      \resumeItem{Advanced Cognitive Neuroscience \& Research Methods}{Independently designed lab section for both courses, leading students through a semester-long experiential learning in R (programming language), leading to a capstone project for each group.}
    \resumeItemListEnd

    \resumeSubheading{Boston University}{Boston, MA}
    {Teaching Assistant}{2011-2012}
    \resumeItemListStart
      \resumeItem{Biomedical Instrumentation I \& II}{Led three sections of laboratory in each semester, guiding students in experiments based on control theory and signal processing.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\vspace{-5pt}
\section{Professional Service}
\begin{itemize}
    \item \textbf{Invited reviewer}: Neural Networks (2018-present); Neural Information Processing Systems (NeurIPS) (2019-present); International Conference on Learning Representations (ICLR) (2020-present)
    \item \textbf{Academic Planning Committee}: Graduate Student representative on a small panel of faculty responsible for overseeing and approving changes in undergraduate and graduate degree program requirements. 2018 - 2019.
\end{itemize}

\vspace{-5pt}
\section{Peer Reviewed Publications}
\begin{enumerate}
    \item \bibentry{chapman_hasselmo_2023} (Accepted)
    \item \bibentry{alexander_nitz_2022}
    \item \bibentry{carstensen_hasselmo_2022}
    \item \bibentry{hasselmo_dannenberg_2020}
    \item \bibentry{alexander_hasselmo_2020}
    \item \bibentry{alexander_hasselmo_2019}
    \item \bibentry{hinman_hasselmo_2019}
    \item \bibentry{monaghan_hasselmo_2017}
    \item \bibentry{hinman_hasselmo_2016}
    \item \bibentry{ferrante_hasselmo_2016}
    \item \bibentry{tsuno_hasselmo_2015}
    \item \bibentry{shay_hasselmo_2015}
    \item \bibentry{raudies_hasselmo_2015a}
    \item \bibentry{jefferson_salat_2015}
    \item \bibentry{gifford_jefferson_2015}
\end{enumerate}


\pagebreak
\vspace{-5pt}
\section{Conference Talks and Posters}
\begin{enumerate}
    \item \bibentry{poster_chapman_chapman_2023}
    \item \bibentry{poster_chapman_chapman_2022a}
    \item \bibentry{poster_chapman_chapman_2022}
    \item \bibentry{poster_chapman_hasselmo_2020a}
    \item \bibentry{poster_chapman_hasselmo_2020}
    \item \bibentry{poster_chapman_chapman_2019}
    \item \bibentry{poster_carstensen_hasselmo_2019}
    \item \bibentry{poster_alexander_hasselmo_2019}
    \item \bibentry{poster_hinman_hasselmo_2018a}
    \item \bibentry{poster_hinman_hasselmo_2018}
    \item \bibentry{poster_carstensen_hasselmo_2018}
    \item \bibentry{poster_alexander_hasselmo_2018}
    \item \bibentry{poster_hinman_hasselmo_2017}
    \item \bibentry{poster_hinman_hasselmo_2016}
    \item \bibentry{poster_tsuno_hasselmo_2015}
    \item \bibentry{poster_monaghan_hasselmo_2015}
    \item \bibentry{poster_hinman_hasselmo_2015}
    \item \bibentry{poster_shay_hasselmo_2014}
    \item \bibentry{poster_ferrante_hasselmo_2014}
    \item \bibentry{poster_climer_eden_2014}
    \item \bibentry{poster_raudies_hasselmo_2013}
    \item \bibentry{poster_hinman_hasselmo_2013}
    \item \bibentry{poster_gifford_jefferson_2013}
    \item \bibentry{poster_ferrante_hasselmo_2013}
    \item \bibentry{poster_chapman_hasselmo_2013}
    \item \bibentry{poster_jefferson_salat_2012}
    \item \bibentry{poster_chapman_salat_2012}
    \item \bibentry{poster_chapman_jefferson_2010}
    \item \bibentry{poster_badaracco_jefferson_2010}
\end{enumerate}

%-----------Awards-----------------
% \section{Honors and Awards}
% \begin{description}[font=$\bullet$]
% \item {Awarded title of Intel Software Innovator - May, 2019}
% \vspace{-5pt}
% \item {Second Runner's Up at TCS EngiNx Engineering Project Innovation Content - September, 2018 }
% \vspace{-5pt}
% \item {Runner's Up at Facebook Developers Circle Hackathon - August, 2017}
% \end{description}

\end{document}